COG-ED Manuscript

### 2021-08-17 06_Paper/COG-ED/Manuscript.Rmd
Calculation of subjective values fully functional

  data_ED <- data_ED[data_ED$step == 6,]

@@

>>>>

  data_ED <- data_ED[data_ED$step == 6,]
  data_ED <- subset(data_ED, select = -c(step))

@@

```{r SVcomputation, echo=FALSE, message=FALSE, warning=FALSE}

  # apply the addition or subtraction of 0.015625 to the last choices

  for (i in 1:nrow(data_ED)) {

    data_ED$fixedlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] == 2.00)] + 1]
    data_ED$flexlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] != 2.00)] + 1]

    if (data_ED$choice[i] == 1) {
      if (data_ED$LBvalue[i] == 2.00) {
        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] + 0.015625, digits = 2)
      } else {
        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] - 0.015625, digits = 2)
      }
    } else {
      if (data_ED$RBvalue[i] == 2.00) {
        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] + 0.015625, digits = 2)
      } else {
        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] - 0.015625, digits = 2)
      }
    }

  }

  # create vector indicating in which rows the data of a new subject begins

  subjectindex <- c(1,which(data_ED$subject != dplyr::lag(data_ED$subject)),nrow(data_ED))

  # create empty data frame for the loop to feed into

  data_SV <- data.frame(subject = character(), sv1 = double(), sv2 = double(), sv3 = double(), sv4 = double())

  # compute subjective values per n-back level and feed into data frame

  for (i in 1:(length(subjectindex)-1)) {

    # initialize empty vectors

    tempone <- double()
    temptwo <- double()
    tempthree <- double()
    tempfour <- double()

    # check for every number, whether it appears in the fixedlevel and flexlevel columns
    # divide flexvalue by 2 if it appears in the fixedlevel columns
    # append 1 if it appears in the flexlevel column

    # for 1-back

        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
          tempone <- append(tempone, data_ED$flexvalue[subjectindex[i]-1 + which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)]/2)
        } else {
          # do nothing
        }

        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
          tempone <- append(tempone, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1))))
        } else {
          # do nothing
        }

    # for 2-back

        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
          temptwo <- append(temptwo, data_ED$flexvalue[subjectindex[i]-1 + which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)]/2)
        } else {
          # do nothing
        }

        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
          temptwo <- append(temptwo, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2))))
        } else {
          # do nothing
        }

    # for 3-back

        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
          tempthree <- append(tempthree, data_ED$flexvalue[subjectindex[i]-1 + which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)]/2)
        } else {
          # do nothing
        }

        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
          tempthree <- append(tempthree, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3))))
        } else {
          # do nothing
        }

    # for 4-back

        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
          tempfour <- append(tempfour, data_ED$flexvalue[subjectindex[i]-1 + which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)]/2)
        } else {
          # do nothing
        }

        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
          tempfour <- append(tempfour, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4))))
        } else {
          # do nothing
        }

    # put the mean subjective value of the three values per n-back level in the respective column and add to data frame

    newdata <- data.frame(data_ED$subject[subjectindex[i]], mean(tempone), mean(temptwo), mean(tempthree), mean(tempfour))
    colnames(newdata) <- names(data_SV)
    data_SV <- rbind(data_SV, newdata)

  }
```
